Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-01-04 supplement.tex
add f4 and csfs figures

\usepackage{fullpage}
\usepackage{listings}
\usepackage{url}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{color}
\usepackage{booktabs}
\usepackage{amsfonts}

@@

\subsection{LD and diversity statistics used in model fits}

@@

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-omni-hapmap-comparison.pdf}
    \caption{
        \textbf{Comparison of LD statistics parsed using two recombination maps}
        The recombination map determines genetic distances between pairs of SNPs,
        so using different maps could result in systematic biases in parsed
        statistics if the maps differ significantly. Here, the solid lines are
        statistics parsed using the HapMapII recombination map, and dashed lines
        are using the OMNI-YRI map. Shading represents 95\% confidence intervals
        from the OMNI map. These two maps results in LD statistics that are
        indistinguishable from one another.
    }
    \label{fig:supp-omni-hapmap-comparison}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-single-origin-fits.pdf}
    \caption{\textbf{Single-origin model fit to LD statistics.}}
    \label{fig:supp-single-origin-fits}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-continuous-migration-fits.pdf}
    \caption{\textbf{Continuous-migration model fit to LD statistics.}}
    \label{fig:supp-continuous-migration-fits}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-merger-without-stem-migration-fits.pdf}
    \caption{\textbf{Merger-without-stem-migration model fit to LD statistics.}}
    \label{fig:supp-merger-without-stem-migration-fits}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-merger-with-stem-migration-fits.pdf}
    \caption{\textbf{Merger-with-stem-migration model fit to LD statistics.}}
    \label{fig:supp-merger-with-stem-migration-fits}
\end{figure}

>>>>

\usepackage{fullpage}
\usepackage{listings}
\usepackage{url}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{color}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{bm}

@@

\subsection{LD and diversity statistics used in model fits}
\label{sec:supp-ld-stats}

@@

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-omni-hapmap-comparison.pdf}
    \caption{
        \textbf{Comparison of LD statistics parsed using two recombination maps}
        The recombination map determines genetic distances between pairs of SNPs,
        so using different maps could result in systematic biases in parsed
        statistics if the maps differ significantly. Here, the solid lines are
        statistics parsed using the HapMapII recombination map, and dashed lines
        are using the OMNI-YRI map. Shading represents 95\% confidence intervals
        from the OMNI map. These two maps results in LD statistics that are
        indistinguishable from one another. Notations for each statistic are
        described in section~\ref{sec:supp-ld-stats} and indexed by populations
        (0: Nama, 1: Mende, 2: Gumuz, 3: Amhara/Oromo, 4: British).
    }
    \label{fig:supp-omni-hapmap-comparison}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-single-origin-fits.pdf}
    \caption{
        \textbf{Single-origin model fit to LD statistics.}
        Predicted vs observed two-locus statistics as a function of genetic
        distance for the single-origin model. Each panel represents a different
        set of two-locus statistics. Solid lines represent estimates using the
        single-origin model. Dashed lines represent observed statistics.
        Notation and indexing of statistics are described in the
        Fig.~\ref{fig:supp-omni-hapmap-comparison} caption.
    }
    \label{fig:supp-single-origin-fits}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-continuous-migration-fits.pdf}
    \caption{
        \textbf{Continuous-migration model fit to LD statistics.}
        Predicted vs observed two-locus statistics as a function of genetic
        distance for the continuous-migration model. Each panel represents a different
        set of two-locus statistics. Solid lines represent estimates using the
        continuous-migration model. Dashed lines represent observed statistics.
        Notation and indexing of statistics are described in the
        Fig.~\ref{fig:supp-omni-hapmap-comparison} caption.
    }
    \label{fig:supp-continuous-migration-fits}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-merger-without-stem-migration-fits.pdf}
    \caption{
        \textbf{Merger-without-stem-migration model fit to LD statistics.}
        Predicted vs observed two-locus statistics as a function of genetic
        distance for the merger-without-stem-migration model. Each panel
        represents a different set of two-locus statistics.
        Solid lines represent estimates using the
        merger-without-stem-migration model.
        Dashed lines represent observed statistics.
        Notation and indexing of statistics are described in the
        Fig.~\ref{fig:supp-omni-hapmap-comparison} caption.
    }
    \label{fig:supp-merger-without-stem-migration-fits}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-merger-with-stem-migration-fits.pdf}
    \caption{
        \textbf{Merger-with-stem-migration model fit to LD statistics.}
        Predicted vs observed two-locus statistics as a function of genetic
        distance for the merger-with-stem-migration model. Each panel
        represents a different set of two-locus statistics.
        Solid lines represent estimates using the
        merger-with-stem-migration model.
        Dashed lines represent observed statistics.
        Notation and indexing of statistics are described in the
        Fig.~\ref{fig:supp-omni-hapmap-comparison} caption.
    }
    \label{fig:supp-merger-with-stem-migration-fits}
\end{figure}

\begin{figure}[ht]
    \centering
    %\includegraphics{figures/supp-FST-panels}
    \caption{
        \textbf{Predicted \bm{$F_{ST}$} between contemporaneous populations over time.}
    }
    \label{fig:supp-FST-panels}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-single-origin.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of modern populations
        and ancient branches from the single-origin model.}
    }
    \label{fig:supp-f4s-single-origin}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-continuous-migration.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of modern populations
        and ancient branches from the continuous-migration model.}
    }
    \label{fig:supp-f4s-continuous-migration}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-merger-without-stem-migration.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of modern populations
        and ancient branches from the merger-without-stem-migration model.}
    }
    \label{fig:supp-f4s-merger-without-stem-migration}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-merger-with-stem-migration.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of modern populations
        and ancient branches from the merger-with-stem-migration model.}
    }
    \label{fig:supp-f4s-merger-with-stem-migration}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-csfs-single-origin.pdf}
    \caption{caption}
    \label{fig:supp-csfs-single-origin}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-csfs-continuous-migration.pdf}
    \caption{caption}
    \label{fig:supp-csfs-continuous-migration}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-csfs-merger-without-stem-migration.pdf}
    \caption{caption}
    \label{fig:supp-csfs-merger-without-stem-migration}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-csfs-merger-with-stem-migration.pdf}
    \caption{caption}
    \label{fig:supp-csfs-merger-with-stem-migration}
\end{figure}
